\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-09 Response.tex

\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in,centering]{geometry}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb}  
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{siunitx}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{color}
\usepackage{bm}
%\usepackage{xr-hyper}
\usepackage{nameref,zref-xr}
\usepackage{hyperref}
\usepackage[]{cleveref} % get fancy referencing

\zexternaldocument{manuscript}
%\externaldocument[]{manuscript}[manuscript.pdf]

% edit cref citations for IEEE format
\crefformat{equation}{(#2#1#3)} % no abbreviation for equation numbers
\Crefformat{equation}{Equation~(#2#1#3)} % no abbreviation for equation numbers
\crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\Crefrangeformat{equation}{(#3#1#4--#5#2#6)}
\crefmultiformat{equation}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
% edit cref citations for IEEE format
\crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\Crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\Crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
\crefmultiformat{figure}{Figs.~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
% for items in a list
\crefformat{enumi}{(#2#1#3)}
\Crefformat{enumi}{Item~(#2#1#3)} 
\crefrangeformat{enumi}{(#3#1#4--#5#2#6)}
\Crefrangeformat{enumi}{Items~(#3#1#4--#5#2#6)}
\crefmultiformat{enumi}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
% Proposition format
\crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
\Crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{prop}{Proposition~#3#1#4--#5#2#6}
\Crefrangeformat{prop}{Propositions~#3#1#4--#5#2#6}
\crefmultiformat{prop}{Propositions~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
% Appendix
\crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
\Crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
\crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
\Crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
\crefmultiformat{appendix}{Appendices~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}

@@

\begin{enumerate}
\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}

The variation of the rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}
We have augmented the proof of~\cref{prop:config_error}, which is given in~\cref{proof:config_error}, to include the definition of the variation as:
\begin{correction}
The infinitesimal variation of a rotation matrix is defined as
\begin{align*}
    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
\end{align*}

\end{correction}

In addition,~\Cref{prop:config_error} was modified to include additional detail on the notation \( \dirDiff{f}{x}\) as
\begin{correction}
The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
	\end{align}
	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
	\end{correction}

\item \textit{This is serious. In section 2, the upper bounds listed in Proposition 4 are given. Well, these should be the properties that your controller guarantees not come from the set D you've defined. Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}

The stability proof has been improved and several modifications have been included in the manuscript:
\begin{itemize}
    \item An additional quadratic property has been derived for \( \Psi \) and shown in~\cref{prop:config_error},
    \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
    \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
\end{itemize}

The revised manuscript, through Propositions 1 and 4, the several properties of the error function and the error variables are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.  Later in the stability proof of Proposition 5, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.  As $D$ is an open neighborhood of the desired attitude, the revised manuscript completes the stability proof.

%Here we present the modifications and provide additional detail. 
%In addition, we duplicate the modifications from the manuscript in this section as well.
%
%In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
%A function \( \psi \) is quadratic on the domain \( D \) about the critical zero \( x_0 \in D \) if there exists two constants \( 0 < b_1 \leq b_2 \) such that
%\begin{align*}
%    b_1 \norm{\text{d} \psi}^2 \leq \psi(x) b_2 \leq \norm{\text{d} \psi}^2 ,
%\end{align*}
%for all \( x \in D \, \setminus \, x_0\)~\cite[Definition 6.28]{bullo2004}.
%To show that \( \Psi \) is quadratic we compute the hessian of \( \Psi \) at the desired attitude \( R = R_d \).
%This additional detail was included in~\cref{prop:config_error}, as shown here:
%\begin{correction}
%     \( \Psi \) is a locally quadratic function on the domain 
%        \begin{align}%\label{eq:psi_quadratic_domain}
%            D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
%        \end{align}
%        and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
%        \begin{align}%\label{eq:psi_bound}
%            n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
%        \end{align}
%\end{correction}
%and proven in~\Cref{proof:config_error}, as shown here:
%\begin{correction}
%    We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
%    \begin{align*}
%        \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
%        &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
%    \end{align*}
%    The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
%    The hessian of \( A(R) \) is computed as 
%    \begin{align*}
%        \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
%        &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
%        &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
%        &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
%    \end{align*}
%    where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
%    The hessian of \( B(R) \) is computed as
%    \begin{align*}
%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
%        & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
%    \end{align*}
%    The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
%    \begin{align*}
%        \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
%        &= - \hat{r} \parenth{R \hat \eta}^T v , \\
%        &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
%        &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
%    \end{align*}
%    where we utilized the hat map property from~\cref{eqn:cross_product}.
%    Similarly, the term \( r^t \delta R^T v \) is simplified as
%    \begin{align*}
%        r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
%        &= r^T \parenth{R^T v}^\wedge \eta .
%    \end{align*}
%    The hessian of \( B(R) \) then becomes
%    \begin{align*}
%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
%        & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
%    \end{align*}
%    Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
%    \begin{align*}
%        \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
%    \end{align*}
%    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
%    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
%\end{correction}
%
%Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
%The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
%Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
%
%The set 
%\[ D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \]
%of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
%The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e. the desired attitude should be sufficiently far away from the constraints. 
%We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
%Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
%
%\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
%\begin{correction}
%    Upper bounds of \( A(R) \) and \( B(R) \) are given by
%    \begin{gather}
%        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
%    \end{gather}
%  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
%  \begin{align*}
%    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
%    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
%  \end{align*}
%\end{correction}
%
%The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
%In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
%We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
%
%\begin{correction}
%    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
%    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
%    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
%    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
%    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
%    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
%\end{correction}
%
%The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
%\begin{correction}
%    Consider the Lyapunov function \( \mathcal{V} \) given by
%    \begin{align*}
%    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
%    \end{align*}
%    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
%
%    From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
%    Using this the Lyapunov function \( \mathcal{V} \) is bounded by
%    \begin{align*} %\label{eqn:v_upper_bound}
%    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
%    \end{align*}
%    where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
%    \begin{align*}
%    W_1 & = \begin{bmatrix}
%        k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
%        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
%        0 & 0 & \frac{1}{2 k_\Delta}
%    \end{bmatrix},\\
%    W_2 & = \begin{bmatrix}
%        k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
%        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
%        0 & 0 & \frac{1}{2 k_\Delta}
%    \end{bmatrix} .
%    \end{align*}
%    The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
%    \begin{align}
%    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
%    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , %\label{eqn:vdot}
%    \end{align}
%    where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
%    The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
%    \begin{align*}
%     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
%    \end{align*}
%    Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
%    \begin{gather*}
%    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
%    \end{gather*}
%    where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
%    \begin{gather*}
%    M = \begin{bmatrix}
%        k_R c & \frac{k_\Omega c}{2} \\
%        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
%    \end{bmatrix} .
%    \end{gather*}

### 2017-01-09 manuscript.tex
Dr. Lee updates on Dropbox

\begin{prop}[Attitude Error Function] \label{prop:config_error}
%We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
Define an attitude error function \( \Psi : \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
\begin{gather}
	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
	e_\Omega = \Omega , \label{eqn:eW}
\end{gather}
with
\begin{gather}
	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
	e_{R_B} = \frac{ \left( R^T v\right)^\wedge r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
\end{gather}	
where \( \alpha \in \R \) is defined as a positive constant and the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
Then, the following properties hold
\begin{enumerate}[(i)]
	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\) on $\SO$.
	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{A}{R} &= \eta \cdot e_{R_A} .
	\end{align}
	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
	\end{align}
    where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
%	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
	\begin{align}
		\norm{e_{R_A}}^2 \leq \frac{A(R)}{b_1} , \label{eqn:psi_lower_bound}
	\end{align}
	where the constant \( b_1 \) is given by \( b_1 = \frac{h_1}{h_2 + h_3} \) for 
	\begin{align*}
		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}.		
	\end{align*}
    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exists constants \( 0 < n_1 \leq n_2 \) such that
    \begin{align}\label{eq:psi_bound}
        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
    \end{align}
    on the domain \( D \) about the desired attitude \( R_d \)
    \begin{align}\label{eq:psi_quadratic_domain}
        D = \braces{R  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} .
    \end{align}
\end{enumerate}
\end{prop}
\begin{proof}
See~\Cref{proof:config_error}
\end{proof}

@@

\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
\end{prop}
\begin{proof}
See~\Cref{proof:adaptive_control}
\end{proof}

@@

We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 

@@

    \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
    &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .

@@

    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\

@@

    & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .

@@

Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as

@@

    \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 

@@

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.

>>>>

\begin{prop}[Attitude Error Function] \label{prop:config_error}
%We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
Define an attitude error function \( \Psi : \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
\begin{gather}
	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
	e_\Omega = \Omega , \label{eqn:eW}
\end{gather}
with
\begin{gather}
	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
	e_{R_B} = \frac{ \left( R^T v\right)^\wedge r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
\end{gather}	
where \( \alpha \in \R \) is defined as a positive constant and the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
Then, the following properties hold
\begin{enumerate}[(i)]
	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\) on $\SO$.
	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
	\end{align}
	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}}.
	\end{align}
%    where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
%	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
	\begin{align}
		\norm{e_{R_A}}^2 \leq \frac{A(R)}{b_1} , \label{eqn:psi_lower_bound}
	\end{align}
	where the constant \( b_1 \) is given by \( b_1 = \frac{h_1}{h_2 + h_3} \) for 
	\begin{align*}
		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}.		
	\end{align*}
    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exist constants \( 0 < n_1 \leq n_2 \) such that
    \begin{align}\label{eq:psi_bound}
        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
    \end{align}
    on the neighborhood $D$ of the desired attitude \( R_d \)
    \begin{align}\label{eq:psi_quadratic_domain}
        D = \braces{R\in\SO  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}
    \end{align}
    for $0<\psi < h_1 $ and $0< \beta<\cos\theta$. 
\end{enumerate}
\end{prop}
\begin{proof}
See~\Cref{proof:config_error}
\end{proof}

@@

\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \min \braces{\sqrt{\frac{2 \lambda_m k_R n_1}{\lambda_M^2}},
	%\sqrt{\frac{2 k_R n_2}{\lambda_M}}, 
	\frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
\end{prop}
\begin{proof}
See~\Cref{proof:adaptive_control}
\end{proof}

@@

We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), namely \( \Hess(\Psi) \),  using the chain rule as 

@@

    \Hess &(\Psi)\cdot (\delta R,\delta R)= (\mathbf{D}_R\parenth{\mathbf{D}_R A \cdot \delta R}\cdot \delta R) B\\
    & + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}} 
    + \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}\\ &+(\mathbf{D}_R\parenth{\mathbf{D}_R B \cdot \delta R}\cdot \delta R) A.

@@

    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\

@@

    & \left. - \frac{\parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha \parenth{r^TR^Tv - \cos \theta}^2}   \right] .

@@

Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as follows. Since $A=0$ and $\mathbf{D}_R A=0$ at $R=R_d$, 

@@

    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 

@@

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
%We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
%Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
%The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.

Consider the open neighborhood $D$ of $R=R_d$ defined in~\cref{proof:config_error} The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
